### 2018-05-15 General WLD combinatorics.tex
finished the proof of that horrible proposition, up to something that should be a lemma and maybe already is

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix \hlfix{which has some actual name and a ref to where you define it}.
\begin{itemize}
  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
    \begin{itemize}
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

@@

By Lemma~\ref{lem susama}, since $I_{i-1}(p)\neq a$, then $I_{i-1} <_{i-1} a$ and no other vertex covered by $p$ lies between them.  In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $x_1x_4-x_2x_3$ is a factor of $r_i$.  Now suppose $a<_i b$ and $p$ is taken before $q$ in $I_i$.  If $I_{i-1}(q)=a$ then $a\in S_i$ and so again $x_1x_4-x_2x_3$ is a factor of $r_i$.  If not, then $I_{i-1}(q) = b$ by Lemma~\ref{lem susama}.  This implies that some other propagator $s$ is associated to $a$ by $I_{i-1}$.  If $s$ also has one end on $(a,b)$ then by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $b$.  However we know $I_i(s) \neq a$ because $I_i(p)=a$, so $I_i(s)=b$ which is also impossible as $I_i(q)=b$.  Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.  Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.  Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(a)=j$.

Finally, then we claim that $I_i(a)\neq j$.  If $i-1=k+1$ then $I_{i-1}(p) = i-1$ and so the construction $I_i$ proceeds as for $I_{i-1}$ without $p$ and cannot differ until $p$, thus the contribution of $a$ cannot change between $I_{i-1}$ and $I_i$.  Now suppose $i-1 \leq_{i-1} k$, then $i \leq_{i} j+1$ \note{I am here, sorry to leave it in the middle but I have things to do with other visitors now}

    \item
  \end{enumerate}
\end{proof}

>>>>

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix \hlfix{which has some actual name and a ref to where you define it}.
\begin{itemize}
  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
    \begin{itemize}
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

@@

By Lemma~\ref{lem susama}, since $I_{i-1}(p)\neq a$, then $I_{i-1} <_{i-1} a$ and no other vertex covered by $p$ lies between them.  In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $x_1x_4-x_2x_3$ is a factor of $r_i$.  Now suppose $a<_i b$ and $p$ is taken before $q$ in $I_i$.  If $I_{i-1}(q)=a$ then $a\in S_i$ and so again $x_1x_4-x_2x_3$ is a factor of $r_i$.  If not, then $I_{i-1}(q) = b$ by Lemma~\ref{lem susama}.  This implies that some other propagator $s$ is associated to $a$ by $I_{i-1}$.  If $s$ also has one end on $(a,b)$ then by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $b$.  However we know $I_i(s) \neq a$ because $I_i(p)=a$, so $I_i(s)=b$ which is also impossible as $I_i(q)=b$.  Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.  Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.  Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(s)=j$.

Finally we want to show $I_i(s)=j$ gives a contradiction.  If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.  If $k+1=j$ then similarly $I_{i}(s)=k+1$ and yet $p$ comes before $s$ around $k$, a contradiction to $I_i(p)=a$.  Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
\[
I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
\]
\note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.  I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}

    \item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$ so the result holds.  Now assume $W$ has at least one propagator.

First we'll show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.  Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$. There exists some $i$ such that $f|\Delta_{I_i}$ but $f\not| \Delta_{I_{i-1}}$ as otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.  If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then by the first direction of the previous part, $I_{i-1}$ cannot make the same association for both propagators $p$ and $q$, but then by the second direction of the previous part, both $p$ and $q$ must be differently assigned between $I_{i-1}$ and $I_i$.  Thus $f$ divides $r_i$.

Next we need to show that $R$ is squarefree.  Suppose $f^2|R$.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.  This contradicts Lemma~\ref{lem susama}.  Now suppose $f$ is a quadratic factor say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.  Since $p$ comes before $q$ on edge $(a,b)$ it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.  Furthermore, we know by the second direction of the previous part that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associate to $b$.  Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$. This is again a contradiction, and so $R$ is squarefree.

Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.  Therefore $R$ is the radical of $\prod_{i=1}^n \Delta_{I_i}$.
  \end{enumerate}
\end{proof}
